---
title: "Data Cleaning"
author: "Group 15"
date: "3/23/2022"
output: html_document
---

# Load All Files 
##You can find all files in google grive: https://drive.google.com/drive/folders/1sesNObh_J6cNO1ht6q3L41js5WIox8R1
```{r}
cur_path = getwd()[1]
data_path = paste(cur_path,'record_data',sep='/')
file_names = list.files(data_path)
file_path <- paste(data_path,file_names,sep = '/')
dfs <- lapply(file_path, read.csv)
files <- gsub('.csv$','',file_names)
names(dfs) <- files
```

```{r}
df1 <- dfs$`annual-number-of-births-by-world-region`
df2 <- dfs$`children-per-woman-by-gdp-per-capita`
df3 <- dfs$`children-per-woman-UN`
df4 <- dfs$`children-per-woman-vs-human-development-index`
df5 <- dfs$`demand-for-family-planning`
df6 <- dfs$`female-labor-force-participation-rates-by-national-per-capita-income`
df7 <- dfs$`fertility-rate-vs-share-of-women-between-25-and-29-years-old-with-no-education`
df8 <- dfs$`fertility-rate-vs-the-share-living-in-extreme-poverty`
df9 <- dfs$`fertility-vs-child-mortality-family-planning-policy`
df10 <- dfs$`fertility-vs-contraception`
df11 <- dfs$`fertility-vs-wanted-fertility`
df12 <- dfs$`maternal-mortality-vs-fertility`
df13 <- dfs$`total-fertility-rate-including-un-projections-through-2100`
df14 <- dfs$`total-fertility-rate-slope-chart`
df15 <- dfs$`womens-educational-attainment-vs-fertility`
# new add csv
df16 <- dfs$`crude-birth-rate`
```

# Merge data and delete unused columns
```{r}
merge_df2 <- Reduce(function(x, y) merge(x, y, by=c("Entity","Year")), list(df6,df7,df9,df10,df12,df15))
merge_df2_new <- merge_df2[-c(3,8,11,12,13,14,16,17,18,21,22,24,25,26,27,29,30)]
merge_df2_new
```

# Rename colmuns
```{r}
colnames(merge_df2_new)
```

```{r}
names <- c("Entity", "Year", "Labor_force_participation_rate", "GDP_per_capita", "Population","Continent", "Children_pre_woman","Percentage_of_female_population_age_25_29_with_no_education","Under_five_mortality", "Fertility_rate", "Contraceptive_prevalence", "Maternal_mortality_ratio", "Mean_years_of_schooling")
colnames(merge_df2_new) <- names
```

# Add "crude-birth-rate.csv" and merge df -- 2022/04/05 changed
```{r}
# Remove "Fertility_rate"
merge_df2_new <- merge_df2_new[-c(10)]
# Add "crude-birth-rate.csv" and merge df
merge_df2_new <- merge(merge_df2_new,df16)
colnames(merge_df2_new)[14] <- "Birth_rate"
# Remove column "code"
merge_df2_new <- merge_df2_new[-c(13)]
merge_df2_new
```


# Identify the continental plate where it is located
```{r}
df <- merge_df2_new[merge_df2_new$Continent != "",][c(1,6)]
```

```{r}
for (i in 1:nrow(merge_df2_new)){
  if (merge_df2_new[i,]$Continent == ""){
    Entity <- merge_df2_new[i,]$Entity
    if (Entity %in% df$Entity){
      Continent <- df[df$Entity == Entity,]$Continent
      merge_df2_new[i,]$Continent <- Continent
    }
  }
}
```

# Delete countries that do not have continental plates
```{r}
plot_df <- merge_df2_new[merge_df2_new$Continent != "",]
plot_df
```

# Some countries have too little data, there are enough countries with 60 years of data 
# keep only those countries
```{r}
plotDF=plot_df
country <- unique(plotDF$Entity)
num_of_years <- c()
for (cont in country){
  num_of_year <- length(unique(plotDF[plotDF$Entity == cont,]$Year))
  num_of_years <- c(num_of_years, num_of_year)
}
num_of_years
```

# Find the names of these countries
```{r}
country <- unique(plotDF$Entity)
wanted_country <- c()
for (cont in country){
  num_of_year <- length(unique(plotDF[plotDF$Entity == cont,]$Year))
  if (num_of_year == 60){
    wanted_country <- c(wanted_country, cont)
  }
}
```

# Delete countries that do not have 60-year numbers
```{r}
new_plotDF <- plotDF[plotDF$Entity %in% wanted_country,]
new_plotDF
```

# Save the cleaned dataset
```{r}
write.csv(new_plotDF,"final_dataset_ALL.csv", row.names = FALSE)
```







